IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-12 review/response_2.tex

		\begin{point}
			The authors are suggested to study the impact of IRS passive beamforming on the waveform design without IRS. For example, they can show the optimized waveforms with versus without IRS to unveil the interplay between them. Or even better, analytically compare the two waveforms.
		\end{point}

		\begin{response}
			Thank you for the suggestion. To see this, we first show one realization of direct channel amplitude (without IRS) and composite channel amplitude (with IRS) for WIT and WPT in Fig.~\ref{fi:channel_amplitude}. It is observed that under the configuration of choice, the WPT-optimized passive beamforming tends to concentrate the channel energy to relatively strong subbands, while the WIT-optimized passive beamforming achieves some balance among all subbands (similar to water-filling at high SNR).

			\begin{figure}[!h]
				\centering
				\resizebox{0.6\columnwidth}{!}{
					\includegraphics{../assets/channel_amplitude}
				}
				\caption{Sorted equivalent subchannel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
				\label{fi:channel_amplitude}
			\end{figure}

@@

		\begin{response}
			We apologize for the inconvenience. The figures have been amplified and the legends have been calibrated.
		\end{response}

		\begin{point}
			It is said that the reference path loss is \SI{35}{\dB} at \SI{1}{\meter}, while for the center frequency at \SI{5.18}{\GHz}, even adopting the free space path loss model also will lead a much sever path loss at \SI{1}{\meter}. It is not clear how the authors calculate this.
			\label{pt:3.3}
		\end{point}

		\begin{response}
			We agree with the reviewer that the reference path loss used in the simulation is faulty and we sincerely apologize for this issue. The parameter \SI{35}{\dB} was considered in some IRS literatures without specifying the operating frequency, and it was taken in the previous simulations without careful consideration. In the corrected manuscript, we instead consider a center frequency at \SI{2.4}{\GHz} that corresponds to a free-space path loss of \SI{40}{\dB} at \SI{1}{\meter}. The path loss used in the simulation is taken from IEEE TGn channel model D \cite{M-Erceg2004} where the slope is \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and \num{3.5} onwards to penalize the channels with large distance.

			In the updated manuscript, we raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi} to compensate the \SI{5}{\dB} difference. Moreover, all plots are re-simulated over \num{200} channel realizations. Please refer to the following specification for details.
			\begin{framed}
				We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{M-Erceg2004}. Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance. All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d. CSCG variables. Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{M-Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$. We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (and one-dimensional search to obtain the R-E region). Each R-E point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
			\end{framed}
		\end{response}

### 2021-08-12 review/letter_2.tex
:package: Add review-related files

\begin{document}
	\begin{letter}{Prof. Liang Xiao \\ Editor \\ IEEE Transactions on Communications \\ ~ \\ Re: Decision on TCOM-TPS-20-1501 (IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model)}
		\opening{Dear Prof. Liang Xiao and Reviewers,}

		We would like to express our appreciation for the time and effort dedicated to the reviewing of our paper. The manuscript has been revised carefully based on your valuable comments and suggestions. In particular, we clarified the motivations and contributions of this work, proved the unit-rank property of the obtained IRS matrix, added two low-complexity designs with near-optimal rate-energy performance, and considered the cases of imperfect cascaded CSIT and finite IRS reflection states. To answer the questions and concerns, we also include a point-to-point response below, which also describes all modifications made to the manuscript. We hope that the revisions are to the satisfaction of the editor and reviewers.

>>>>

\begin{document}
	\begin{letter}{Prof. Liang Xiao \\ Editor \\ IEEE Transactions on Communications \\ ~ \\ Re: Decision on TCOM-TPS-21-0553 (IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model)}
		\opening{Dear Prof. Liang Xiao and Reviewers,}

		We would like to express our appreciation for the time and effort dedicated to the reviewing of our paper. The manuscript has been revised carefully based on your valuable comments and suggestions. In particular, we added computational complexity analysis for all proposed algorithms, addressed the optimality issue regarding Algorithm 4, discussed the convergence conditions in Algorithm 5, emphasized the design challenge introduced by passive beamforming and nonlinear EH model, and updated the simulation parameters and reference list. To answer the questions and concerns, we also include a point-to-point response below to discuss all modifications made to the manuscript. We hope that the revisions are to the satisfaction of the editor and reviewers.
